Clustering galaxies at 0.5 < $z$ < 1: data mining approach

### 2016-04-12 sections0.0/intro0.0.tex
Adding new lines about usage of SOM in astronomy

Advances in imaging techniques, and photometry and spectroscopy devises help to have higher resolution data and more detailed SED. 
Thus, the variations between SEDs become more clear and the classification of galaxies became more complicated.
Many groups used data from nearby galaxies in order to composite a thorough template for categorizing the spectral type of the galaxies~\citep[e.g.][]{Kinney94}~\citep[][hereafter K96]{Kinney96}~\citep[][]{Bershady00}.%and more references
These templates are mostly restricted to wavelengths from near-IR to ultraviolet (UV), so they contain main features from physical properties of galaxies i.e. age, star formation rate (SFR), stellar mass, wide range of the stellar population, interstellar medium (ISM)'s absorption and emission lines, and extinction from ISM of the galaxies.

One of the main usage of the SED templates is finding the morphological type of high redshift galaxies. 
However, since not two galaxies, even with same morphology, are exactly the same, classifying the SED of the galaxies are a challenge.
Many fitting methods are developed and used to find the best matches of template for each SED.
$\chi^2$ minimizing method is the most commonly used method to do so. 
Artificial neural networks (ANNs) are the other method to find the morphological type of the galaxies based on their SED.

@@

@@

In this paper, we used data from K96 template to train an unsupervised neural network.
The network clustered the SEDs and mapped those clusters and their relative relations.
We compared our results with K96 galaxies classification.
Then we classify the SED of the sample of 142 galaxies using the constructed SOM.
 In Section $\S$~\ref{sec: data}, we present the data. We describe the SOM in Section $\S$~\ref{sec: method}. The results of the SED classifications are shown in Section $\S$~\ref{sec: result} and discussed in Section $\S$~\ref{sec: diss}. In Section $\S$~\ref{sec: summary}, we present the summary of our conclusion and the future works in this subject.

>>>>

Advances in imaging techniques, and photometry and spectroscopy devises help to have higher resolution data and more detailed SED. 
Thus, the variations between SEDs become more clear and the classification of galaxies became more complicated.
Many groups used data from nearby galaxies in order to composite a thorough template for categorizing the spectral type of the galaxies~\citep[e.g.][]{Kinney93}~\citep[][hereafter K96]{Kinney96}~\citep[][]{Bershady00}.%and more references
These templates are mostly restricted to wavelengths from near-IR to ultraviolet (UV), so they contain main features from physical properties of galaxies i.e. age, star formation rate (SFR), stellar mass, wide range of the stellar population, interstellar medium (ISM)'s absorption and emission lines, and extinction from ISM of the galaxies.

One of the main usage of the SED templates is finding the morphological type of high redshift galaxies. 
However, since not two galaxies, even with same morphology, are exactly the same, classifying the SED of the galaxies are a challenge.
Many fitting methods are developed and used to find the best matches of template for each SED.
$\chi^2$ minimizing method is the most commonly used method to do so. 
Artificial neural networks (ANNs), K-mean clustering, and principle component analysis are the other methods to cluster and classifying the morphological type of the galaxies based on their SED \citep[e.g.][]{Allen13,Ordov14,Shi15}.

@@

%SOM in Astronomy
The utilization of the SOM in astronomy dates back to 1990s. 
\citet[][]{Odewahn92}, \citet[][]{Hernandez94}, and \citet[][]{Murtagh95} were among the first studies in astronomy that used SOM for their studies.
From classifying quasars' spectra to star/galaxy classifications, from gamma-ray bursts clustering to classificationf of light curves, this method have been used in various aspects in astronomy \citep[e.g.][]{Maehoenen95, Miller96,Andreon00,Balastegui01,Rajaniemi02,Brett04,Scaringi09}.
\citet{Geach12} used COSMOS data to demonstrate two of main application of SOMs; object classification and clustering, and photometric redshift estimation. 
The later one were subject of many studies \citep[e.g.][]{Kind14a}
\citet{In12} introduced a new clustering tool which is based on SOM method to analysing large data of spectra.
They used $\sim 60000$ spectra from the Sloan Digital Sky Survey \citep[SDSS;][]{Abazajian09}
to test their tool, and created very large SOMs to analyse the type of spectra/objects.
They also generated SOMs from quasar spectra in order to find unusual types of quasars spectra. Later \citet{Meusinger16} used these SOMs and updated data from SDSS and other surveys and found a new class of quasars.
The other application of the SOM is to find outliers or errors in the data.
\citet{Fustes13} used this method to produced a package to classify results from GAIA surveys and find the outlier or errors in the instruments or pipelines.

@@

In this paper, we used data from K96 template to train an unsupervised neural network.
The network clustered the SEDs and mapped those clusters and their relative relations.
We compared our results with K96 galaxies classification.
Then we classify the SED of the sample of 142 galaxies using the constructed SOM.

 In Section $\S$~\ref{sec: data}, we present the data. We describe the SOM in Section $\S$~\ref{sec: method}. The results of the SED classifications and comparing them with previous studoes are shown in Section $\S$~\ref{sec: result}. In Section $\S$~\ref{sec: summary}, we present the summary of our conclusion and the future works in this subject.
